### 2024-01-21 analysis.qmd
Latest regression table

# Data Wrangling
```{r Getting and wrangling data}
    gs4_deauth()
    dat <- read_sheet("https://docs.google.com/spreadsheets/d/1r6IcGtlTOaAFHxJYgnuGM6IEiJhaIoDBhxEfRIhZEeI/edit?usp=sharing") 
    dat <- dat[-c(1), ] #getting rid of first row
    #working.dat <- dat.wrang(dat)
```

```{r Data Wrangling Genres}
    dat.dis <- dat.genres(dat)$dat.g %>%
          mutate(across(Classical:Metal, function(x) {if_else(x < 3, 1, 0)})) %>% 
          rowwise() %>% 
          mutate(num.dis = sum(c_across(Classical:Metal), na.rm = T)) %>% 
          ungroup() %>% 
          mutate(bin.dis = if_else(num.dis == 0, 1, 0))
    head(dat.dis)
         reg.dat <- dat.demog(dat) %>% 
          left_join(dat.dis)
```

@@

```{r Bivariate Plots (Categorical Tolerance)}
      a <- reg.dat$bin.dis
      plot.dat <- reg.dat %>% 
        na.omit() %>% 
        group_by(Age) %>% 
        summarize(y = sum(bin.dis)) %>% 
        mutate(t = table(reg.dat$Age)) %>% 
        mutate(prop = round(y / t, 3)) %>% 
        dplyr::select(c("Age", "prop"))
      plot.dat$Age <- factor(plot.dat$Age, 
                             labels = c("18 - 19", "20 - 24",
                                        "25 - 29", "30 - 34", "35 - 39", "40 - 44",
                                        "45 - 49", "50 - 54", "55 - 59", "60 - 64",
                                        "65 - 69", "70+"))
      make.bar(plot.dat, x = 2, y = 1, "cat-tol-age.png", m = mean(a, na.rm = T))

@@

```{r Bivariate Plots (N. of Dislikes)}
      a <- reg.dat$num.dis[!reg.dat$num.dis %in% 0]
      plot.dat <- reg.dat %>% 
        na.omit() %>% 
        dplyr::filter(num.dis > 0) %>% 
        group_by(Age) %>% 
        summarize(m = mean(num.dis)) 
      plot.dat$Age <- factor(plot.dat$Age, 
                             labels = c("18 - 19", "20 - 24",
                                        "25 - 29", "30 - 34", "35 - 39", "40 - 44",
                                        "45 - 49", "50 - 54", "55 - 59", "60 - 64",
                                        "65 - 69", "70+"))
      make.bar(plot.dat, x = 2, y = 1, "num-dis-age.png", m = mean(a, na.rm = T))

@@

```{r Regression Analysis}
     m1 <- zeroinfl(num.dis ~ Educ + Age + Gender + 
                         Race + polviews + year |
                         Educ + Age + Age2 + Gender + Race + polviews + year, 
                         data = reg.dat
               )
     tab_model(m1, transform = NULL, file = here("Tabs", "zinf-reg.html"))
```

>>>>

# Data Wrangling
```{r Getting and wrangling data}
    gs4_deauth()
    dat <- read_sheet("https://docs.google.com/spreadsheets/d/1r6IcGtlTOaAFHxJYgnuGM6IEiJhaIoDBhxEfRIhZEeI/edit?usp=sharing") 
    dat <- dat[-c(1), ] #getting rid of first row
```

```{r Data Wrangling Genres}
    dat.dis <- dat.genres(dat)$dat.g %>%
          mutate(across(Classical:Metal, function(x) {if_else(x < 3, 1, 0)})) %>% 
          rowwise() %>% 
          mutate(num.dis = sum(c_across(Classical:Metal), na.rm = T)) %>% 
          ungroup() %>% 
          mutate(bin.dis = if_else(num.dis == 0, 1, 0))
    head(dat.dis)
         reg.dat <- dat.demog(dat) %>% 
          left_join(dat.dis) %>% 
          mutate(Man = if_else(Gender == "Man", 1, 0)) %>% 
          mutate(Moderate = if_else(polviews < 3 | polviews > 5, 1, 0)) %>% 
          mutate(Black = if_else(Race == "Black", 1, 0)) %>% 
          mutate(Age_30_to_49 = if_else(Age > 3 & Age < 8, 1, 0)) %>% 
          rename(Survey_Year = year, Political_Ideology = polviews, Education = Educ) %>% 
          mutate(Survey_Year = factor(Survey_Year, labels = c("2021", "2023", "2023")))
```

@@

```{r Bivariate Bar Plots (Categorical Tolerance)}
      a <- reg.dat$bin.dis
      plot.dat <- reg.dat %>% 
        na.omit() %>% 
        group_by(Age) %>% 
        summarize(y = sum(bin.dis)) %>% 
        mutate(t = table(reg.dat$Age)) %>% 
        mutate(prop = round(y / t, 3)) %>% 
        dplyr::select(c("Age", "prop"))
      plot.dat$Age <- factor(plot.dat$Age, 
                             labels = c("18 - 19", "20 - 24",
                                        "25 - 29", "30 - 34", "35 - 39", "40 - 44",
                                        "45 - 49", "50 - 54", "55 - 59", "60 - 64",
                                        "65 - 69", "70+"))
      make.bar(plot.dat, x = 2, y = 1, "cat-tol-age.png", m = mean(a, na.rm = T))

@@

```{r Bivariate Bar Plots (N. of Dislikes)}
      a <- reg.dat$num.dis[!reg.dat$num.dis %in% 0]
      plot.dat <- reg.dat %>% 
        na.omit() %>% 
        dplyr::filter(num.dis > 0) %>% 
        group_by(Age) %>% 
        summarize(m = mean(num.dis)) 
      plot.dat$Age <- factor(plot.dat$Age, 
                             labels = c("18 - 19", "20 - 24",
                                        "25 - 29", "30 - 34", "35 - 39", "40 - 44",
                                        "45 - 49", "50 - 54", "55 - 59", "60 - 64",
                                        "65 - 69", "70+"))
      make.bar(plot.dat, x = 2, y = 1, "num-dis-age.png", m = mean(a, na.rm = T))

@@

```{r Regression Analysis}
     m1 <- zeroinfl(num.dis ~ 
                      Age  + Political_Ideology + Race |
                      Education + Age_30_to_49 + Man + Moderate + Black + Survey_Year,
                      data = reg.dat)
     m2 <- zeroinfl(num.dis ~ 
                      Age  + Political_Ideology + Race |
                      Education*Survey_Year + Age_30_to_49*Survey_Year + 
                      Man*Survey_Year + Moderate*Survey_Year + Black*Survey_Year,
                      data = reg.dat)
     tab_model(m1, transform = NULL, file = here("Tabs", "zinf-reg.html"), 
               auto.label = TRUE, dv.labels = "", 
               show.zeroinf = TRUE, show.aic = TRUE, show.loglik = TRUE,
               show.ci = FALSE)
     webshot(here("Tabs", "zinf-reg.html"), here("Tabs", "zinf-reg.png"))
```
